\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-22 papers/jss/article.Rnw
John Wilkes feels we should end the session in table1 with class(p) instead of beginning with it.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@822 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

%% TODO(de) Can we make this not break the width of the page?
\noindent
\begin{table}
\begin{tabular}{p{.40\textwidth}p{0.55\textwidth}}
\toprule
Schema : \texttt{addressbook.proto} & Example R Session\\
\cmidrule{1-2}
\begin{minipage}{.40\textwidth}
\vspace{2mm}
\begin{example}
package tutorial;
message Person {
 required string name = 1;
 required int32 id = 2;
 optional string email = 3;
 enum PhoneType {
   MOBILE = 0; HOME = 1;
   WORK = 2;
 }
 message PhoneNumber {
   required string number = 1;
   optional PhoneType type = 2;
 }
 repeated PhoneNumber phone = 4;
}
\end{example}
\vspace{2mm}
\end{minipage} & \begin{minipage}{.55\textwidth}
<<echo=TRUE>>=
library(RProtoBuf)
p <- new(tutorial.Person,id=1,name="Dirk")
class(p)
p$name
p$name <- "Murray"
cat(as.character(p))
serialize(p, NULL)
@
\end{minipage} \\
\bottomrule
\end{tabular}
\caption{The schema representation from a \texttt{.proto} file for the
  \texttt{tutorial.Person} class (left) and simple R code for creating
  an object of this class and accessing its fields (right).}
\label{tab:proto}
\end{table}

>>>>

%% TODO(de) Can we make this not break the width of the page?
\noindent
\begin{table}
\begin{tabular}{p{.40\textwidth}p{0.55\textwidth}}
\toprule
Schema : \texttt{addressbook.proto} & Example R Session\\
\cmidrule{1-2}
\begin{minipage}{.40\textwidth}
\vspace{2mm}
\begin{example}
package tutorial;
message Person {
 required string name = 1;
 required int32 id = 2;
 optional string email = 3;
 enum PhoneType {
   MOBILE = 0; HOME = 1;
   WORK = 2;
 }
 message PhoneNumber {
   required string number = 1;
   optional PhoneType type = 2;
 }
 repeated PhoneNumber phone = 4;
}
\end{example}
\vspace{2mm}
\end{minipage} & \begin{minipage}{.55\textwidth}
<<echo=TRUE>>=
library(RProtoBuf)
p <- new(tutorial.Person,id=1,name="Dirk")
p$name
p$name <- "Murray"
cat(as.character(p))
serialize(p, NULL)
class(p)
@
\end{minipage} \\
\bottomrule
\end{tabular}
\caption{The schema representation from a \texttt{.proto} file for the
  \texttt{tutorial.Person} class (left) and simple R code for creating
  an object of this class and accessing its fields (right).}
\label{tab:proto}
\end{table}
